%-------------------------
% Jake's Resume Style — Shaptak Naskar
% Compile with: pdflatex ShaptakCV.tex
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[margin=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING-----------
\begin{center}
    \textbf{\Huge \scshape Shaptak Naskar} \\ \vspace{1pt}
    \small Kolkata, India $|$
    \href{mailto:ddtectiv.ddip2017@gmail.com}{\underline{ddtectiv.ddip2017@gmail.com}} $|$
    \href{https://linkedin.com/in/shaptak}{\underline{linkedin.com/in/shaptak}} $|$
    \href{https://github.com/ShaptakNaskar}{\underline{github.com/ShaptakNaskar}} $|$
    \href{https://sappy-dir.vercel.app/}{\underline{sappy-dir.vercel.app}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Greater Kolkata College of Engineering and Management}{Kolkata, India}
      {Bachelor of Technology -- Computer Science; GPA: 7.20}{August 2022 -- July 2025}
    \resumeSubheading
      {Engineering Institute for Junior Executives}{Kolkata, India}
      {Diploma -- Electronics and Telecommunication; GPA: 7.80}{June 2019 -- August 2022}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Project Intern}{Nov 2025 -- Mar 2026}
      {MindEdge Solutions}{Kolkata, India}
      \resumeItemListStart
        \resumeItem{Helped build a full-featured \textbf{AI Meeting Summarizer} using Groq Whisper v3 and GPT-OSS-120B that automatically generates Minutes of Meeting (MOM), transcripts, and actionable to-do lists from audio/video recordings; integrated MOM sharing and collaborative review workflows.}
        \resumeItem{Developed an AI-powered \textbf{Content Calendar Generator} for digital marketing — accepts client name, website, and date range to produce a holiday-inclusive content calendar with post schedules, captions, hashtags, AI-generated image prompts, and logo-embedded image exports.}
        \resumeItem{Engineered a \textbf{Business Card to vCard Converter} using GPT-4o-mini for OCR-based contact extraction; integrated webcam capture via getUserMedia and Base64 file upload, reducing manual contact entry from minutes to seconds at $\sim$\$0.01 per scan with no backend required.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Auto AI Brochure Generator} $|$ \emph{Node.js, AI, GUI, Automation}}{}
          \resumeItemListStart
            \resumeItem{Automated system that generates comprehensive digital marketing proposals from incoming email inquiries and website analysis using AI, eliminating hours of manual proposal writing.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Content Automation Engine} $|$ \emph{Node.js, AI, GUI, Digital Marketing}}{}
          \resumeItemListStart
            \resumeItem{GUI-based social media automation platform that manages the full lifecycle of content creation and publication — from AI-assisted drafting to scheduled cross-platform posting.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{ADB Commander} $|$ \emph{Electron, Windows, Linux, Cross-platform GUI}}{}
          \resumeItemListStart
            \resumeItem{Modern cross-platform GUI frontend for the Android Debug Bridge (ADB), simplifying device management and debugging workflows without requiring command-line expertise.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{WeatherMan} $|$ \emph{Flutter, Dart, Android, REST API}}{}
          \resumeItemListStart
            \resumeItem{Glassmorphic Android weather application inspired by iOS Weather UI; integrates a live weather API with smooth animations and a modern design system built with Flutter.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, Dart, HTML/CSS, Bash} \\
     \textbf{Frameworks \& Libraries}{: React.js, Node.js, Express.js, Flutter, MongoDB (MERN Stack)} \\
     \textbf{AI \& APIs}{: OpenAI API (GPT-4o-mini), Groq Whisper v3, GPT-OSS-120B, REST API integration} \\
     \textbf{Tools \& Platforms}{: Git, GitHub, Vercel, ExifTool, Android Debug Bridge (ADB), Vite, Tailwind CSS} \\
     \textbf{Areas}{: Full Stack Web Development, Android Development, Automation Scripting, AI-Assisted Development}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications \& Training}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{30-Hour Cybersecurity Training} --- Ardent Computech Pvt. Ltd., Mar 2024.
     Threat detection, encryption, secure networks, and vulnerability mitigation. \\
     \textbf{30-Hour AI \& ML with Python Training} --- Ardent Computech Pvt. Ltd., Mar 2024.
     Data processing, model training/deployment, predictive analytics with NumPy \& scikit-learn. \\
     \textbf{Cybersecurity Virtual Internship (10 Weeks)} --- AICTE, Feb 2023.
     Ethical hacking, firewall configuration, incident response, and enterprise security tooling.
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
